Learning Discrete Bayesian Networks from Continuous Data

### 2015-12-01 BN_discretizer_paper.tex
quantative ->qualitative

To quantatively assess the sensitivity of each method to the number and position of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the discretization methods are:

>>>>

To qualitatively assess the sensitivity of each method to the number and position of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the discretization methods are:
